National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs

### 2020-11-18 Manuscript.Rmd
small fixes

First, previous research has frequently operationalised spirituality using measures of well-being. For example, The Daily Spiritual Experience Scale, which is widely used in spiritual mental health research, includes items such as "I feel thankful for my blessings" and "I feel deep inner peace or harmony" to measure spirituality [@Underwood2002-hg]. As Koenig observes, it is unsurprising that spirituality predict well-being when the same items are used to measure both constructs. Koenig aptly describes this approach as "tautological" [@Koenig2008-lv]. Indeed, recent systematic-review of spirituality/mental health research found that nearly 45% of previous studies employe tautological scales [@Garssen2016-kb]. The first challenge, then, is to define measures of spirituality that are not well-being measures dressed up in other words.

>>>>

First, previous research has frequently operationalised spirituality using measures of well-being. For example, The *Daily Spiritual Experience Scale*, which is widely used in spiritual mental health research, includes items such as "I feel thankful for my blessings" and "I feel deep inner peace or harmony" to measure spirituality [@Underwood2002-hg]. As Koenig observes, it is unsurprising that spirituality predict well-being when the same items are used to measure both constructs. Koenig aptly describes this approach as "tautological" [@Koenig2008-lv]. Indeed, recent systematic-review of spirituality/mental health research found that nearly 45% of previous studies employe tautological scales [@Garssen2016-kb]. The first challenge, then, is to define measures of spirituality that are not well-being measures dressed up in other words.

### 2020-11-18 Manuscript.tex
small fixes

First, previous research has frequently operationalised spirituality using measures of well-being. For example, The Daily Spiritual Experience Scale, which is widely used in spiritual mental health research, includes items such as \enquote{I feel thankful for my blessings} and \enquote{I feel deep inner peace or harmony} to measure spirituality (Underwood \& Teresi, 2002). As Koenig observes, it is unsurprising that spirituality predict well-being when the same items are used to measure both constructs. Koenig aptly describes this approach as \enquote{tautological} (Koenig, 2008). Indeed, recent systematic-review of spirituality/mental health research found that nearly 45\% of previous studies employe tautological scales (Garssen et al., 2016). The first challenge, then, is to define measures of spirituality that are not well-being measures dressed up in other words.

>>>>

First, previous research has frequently operationalised spirituality using measures of well-being. For example, The \emph{Daily Spiritual Experience Scale}, which is widely used in spiritual mental health research, includes items such as \enquote{I feel thankful for my blessings} and \enquote{I feel deep inner peace or harmony} to measure spirituality (Underwood \& Teresi, 2002). As Koenig observes, it is unsurprising that spirituality predict well-being when the same items are used to measure both constructs. Koenig aptly describes this approach as \enquote{tautological} (Koenig, 2008). Indeed, recent systematic-review of spirituality/mental health research found that nearly 45\% of previous studies employe tautological scales (Garssen et al., 2016). The first challenge, then, is to define measures of spirituality that are not well-being measures dressed up in other words.
